``` {r, results=T}
datatel <- read.csv("Telecom Data.csv")
typeof(datatel)
head(datatel)
```

Does a high number of active subscribers lead to a low monthly revenue?
```{r, results=T}
actsubdata <- subset(datatel, datatel$ActiveSubs > 1)
head(actsubdata)
sum(is.na(actsubdata$ActiveSubs))

```
No null values
```{r, results=T}
minsub <- 0
nosub <- 0
manysub <- 0

for (i in actsubdata$ActiveSubs){
  if (i< 1){
    nosub=nosub+1
  }else if (i == 1){
    minsub=minsub+1
  }else if (i > 1) {
    manysub=manysub+1
  }
  i=i+1
}

print(nosub)
print(manysub)
print(minsub)
nrow(actsubdata$MonthlyRevenue)
nrow(actsubdata$ActiveSubs)
```

correlation between 2 variables
```{r, results=T}
cor.test(actsubdata$MonthlyRevenue, actsubdata$ActiveSubs, method='spearman')
```

The output is -0.025. 
Negative sign indicates that monthly revenue and active subscribers vary in the opposite direction. The output is also closer to 0. This means there is only slight change in Monthly Revenue of telecom company as the active subscribers vary. 


```{r, results=T}

#Plot with statistical results

library(ggplot2)
ggplot(data = actsubdata) + 
  geom_smooth(mapping = aes(x = ActiveSubs, y = MonthlyRevenue), color="brown") +theme_classic()
```

From the graph we can see that as active subscribers increases monthly revenue is decreasing slightly.

```{r, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = actsubdata, x = "ActiveSubs", y = "MonthlyRevenue",
          conf.int = TRUE, color="brown")
```


```{r, results=T}
churndata <- subset(datatel, datatel$Churn == "Yes")
head(churndata)
nrow(churndata)
sum(is.na(churndata$MonthlyRevenue))
sum(is.na(churndata$OverageMinutes))

```
We can see there are 70 NA values in monthly revenue and overageminutes columns when churn is yes
Lets remove those NA values

```{r, results=T}
churndata2 <- na.omit(churndata)
head(churndata2)
nrow(churndata2)
sum(is.na(churndata2$MonthlyRevenue))
sum(is.na(churndata2$OverageMinutes))
```
We have removed all the null values.
Now lets do correlation
```{r, results=T}
cor.test(churndata2$MonthlyRevenue, churndata2$OverageMinutes, method='spearman')
```
The output is 0.5911 which is approximately 0.6. 
As the sign is positive, we can say that monthly revenue and overage minutes vary postively when there is churn. That is, the as the overage minutes increases, monthly revenue also increases. 

```{r, results=T}

#Plot with statistical results

library(ggplot2)
ggplot(data = churndata2) + 
  geom_smooth(mapping = aes(x = OverageMinutes, y = MonthlyRevenue), color="brown") + theme_classic()
```
From the graph we can see that as Overage Minutes increased, Monthly revenue also increased. 

```{r, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = churndata2, x = "OverageMinutes", y = "MonthlyRevenue",
          conf.int = TRUE, color="brown")
```

Now lets plot when there is no churn, that is when there is retention of customers. 

```{r, results=T}
retentiondata <- subset(datatel, datatel$Churn == "No")
head(retentiondata)
nrow(retentiondata)
sum(is.na(retentiondata$MonthlyRevenue))
sum(is.na(retentiondata$OverageMinutes))

```

We can see there are 86 NA values in monthly revenue and overageminutes columns when there is no churn.
Lets remove those NA values

```{r, results=T}
retentiondata2 <- na.omit(retentiondata)
head(retentiondata2)
nrow(retentiondata2)
sum(is.na(retentiondata2$MonthlyRevenue))
sum(is.na(retentiondata2$OverageMinutes))
```

We have removed all the null values.
Now lets do correlation
```{r, results=T}
cor.test(retentiondata2$MonthlyRevenue, retentiondata2$OverageMinutes, method='spearman')
```
Even when there is retention the output is 0.56, we can say the that Monthly revenue varies postively as overage minutes varies. 
```{r, results=T}

#Plot with statistical results

library(ggplot2)
ggplot(data = retentiondata2)+
  geom_smooth(mapping = aes(x = OverageMinutes, y = MonthlyRevenue), color="dark green" ) + theme_classic()
```
From the graph we can see that as Overage Minutes increases, Monthly revenue also increases. 
```{r, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = retentiondata2, x = "OverageMinutes", y = "MonthlyRevenue",
          conf.int = TRUE, color="dark green")
```

```{r, results=T}
datacorr <- datatel[ , c("MonthlyRevenue","MonthlyMinutes", "TotalRecurringCharge","CustomerCareCalls","ThreewayCalls","ReceivedCalls","OutboundCalls","MonthsInService","HandsetPrice","CreditRating")]   
head(datacorr)
nrow(datacorr)
sum(is.na(datacorr))
```
```{r, results=T}
datacorr2 <- na.omit(datacorr)
nrow(datacorr2)
sum(is.na(datacorr2))
```

```{r, results=T}
# load package
#install.packages("ggstatsplot")
#install.packages("ggcorrplot")

library(ggstatsplot)
library(ggcorrplot)
library(corrplot)

# correlogram
ggstatsplot::ggcorrmat(
  data = datacorr2,
  type = "nonparametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue") 
)

```

```{r,results="show"}
cor_1=subset(datatel,select=c("MonthlyRevenue","MonthlyMinutes", "TotalRecurringCharge","CustomerCareCalls","ThreewayCalls","ReceivedCalls","OutboundCalls"))
corrplot.mixed(cor(cor_1))
```

