Does a high number of active subscribers lead to a low monthly revenue?
```{r Active_Subscribers, echo=T, results=T}
Telecom_Data <- read.csv("Telecom Data.csv")
```

Subsetting the dataframe in to another variable to check active subscribers.
```{r, results=T}
actsubdata <- subset(Telecom_Data, Telecom_Data$ActiveSubs > 1)
head(actsubdata)
sum(is.na(actsubdata$ActiveSubs))

```
There are no NA values in the data frame.

Analysing correlation between active subscribers and monthly revenue to find whether high active subscribers lead to low monthly revenue.
```{r, results=T}
cor.test(actsubdata$MonthlyRevenue, actsubdata$ActiveSubs, method='spearman')
```
The output is -0.025. 
Negative sign indicates that monthly revenue and active subscribers vary in the opposite direction. The output is also closer to 0. This means, active subscribers have nothing to do with the monthly revenue of the telecom company. Yet, we can see a slight negative relationship between them where, as active subscribers increase monthly revenue decreases slightly.
```{r, echo=T, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = actsubdata, x = "ActiveSubs", y = "MonthlyRevenue",
          conf.int = TRUE, color="blue", xlab="Active Subscribers", ylab="Monthly Revenue of the Telecom company", title="Scatter plot of Active Subscribers vs Monthly Revenue")
```
The above scatter plot shows that there is a negative correlation between Active subscribers and monthly revenue. 


Bi-variate Analysis.
```{r Bivariate-Analysis, echo=T, results=T}
Telecom_Data <- read.csv("Telecom Data.csv")
typeof(Telecom_Data)
head(Telecom_Data)
```

Subsetting dataframe for churn = yes.
```{r Correlation Analysis, echo=T, results=T}
churndata <- subset(Telecom_Data, Telecom_Data$Churn == "Yes")
head(churndata)
nrow(churndata)
sum(is.na(churndata$MonthlyRevenue))
sum(is.na(churndata$OverageMinutes))
```
We can see there are 70 NA values in monthly revenue and overageminutes columns when churn is yes.

Lets remove those NA values
```{r, echo=T, results=T}
churndata2 <- na.omit(churndata)
head(churndata2)
nrow(churndata2)
sum(is.na(churndata2$MonthlyRevenue))
sum(is.na(churndata2$OverageMinutes))
```


We have removed all the null values.

Correlation Analysis of Monthly Revenue and Overage Minutes for churned customers. 
```{r,echo=TRUE,results=T}
cor.test(churndata2$MonthlyRevenue, churndata2$OverageMinutes, method='spearman')
```


The output is 0.5911, which is approximately 0.6. 
As the sign is positive, we can say that monthly revenue and overage minutes vary postively when there is churn. That is, as the overage minutes increases, monthly revenue also increases. 

Plotting line graph to see the relation between the monthly revenue and overage minutes for churned customers.
```{r, echo=True, results=T}

#Plot with statistical results

library(ggplot2)
ggplot(data = churndata2) + 
  geom_smooth(mapping = aes(x = OverageMinutes, y = MonthlyRevenue, color="Brown")) + theme_classic()+
  xlab("Overage minutes used by the customer") + ylab("Monthly revenue of the Telecom company ") 
```
From the graph we can see that as Overage Minutes increased, Monthly revenue also increased. 

Scatter plot for overage minutes and monthly revenue for churned customers.
```{r, echo=True, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = churndata2, x = "OverageMinutes", y = "MonthlyRevenue",
          conf.int = TRUE, color="brown", xlab="Overage Minutes used by customer", ylab="Monthly Revenue of the Telecom company", title="Scatter plot of Overage Minutes vs Monthly Revenue for churned customers")
```
The scatter graph in the aforementioned section illustrates the positive correlation between customer overage minutes consumed and the telecom sector's monthly income for customers who churn.

Now lets plot when there is no churn, that is when there is retention of customers. 
Subsetting the dataframe for churn=No
```{r, echo=, results=T}
retentiondata <- subset(Telecom_Data, Telecom_Data$Churn == "No")
head(retentiondata)
nrow(retentiondata)
sum(is.na(retentiondata$MonthlyRevenue))
sum(is.na(retentiondata$OverageMinutes))

```

We can see there are 86 NA values in monthly revenue and overageminutes columns when there is no churn.

Lets remove those NA values
```{r, echo=T, results=T}
retentiondata2 <- na.omit(retentiondata)
head(retentiondata2)
nrow(retentiondata2)
sum(is.na(retentiondata2$MonthlyRevenue))
sum(is.na(retentiondata2$OverageMinutes))
```


We have removed all the null values.

Now lets do correlation
```{r, echo=T, results=T}
cor.test(retentiondata2$MonthlyRevenue, retentiondata2$OverageMinutes, method='spearman')
```

Even when there is retention the output is 0.56, we can say the that Monthly revenue varies postively as overage minutes varies. 


```{r, echo=T, results=T}

#Plot with statistical results

library(ggplot2)
ggplot(data = retentiondata2)+
  geom_smooth(mapping = aes(x = OverageMinutes, y = MonthlyRevenue), color="dark green" ) + theme_classic() + xlab("Overage minutes used by the customer") + ylab("Monthly revenue of the Telecom company ")
```


From the graph we can see that as Overage Minutes increases, Monthly revenue also increases. 


```{r, echo=T, results=T}
#install.packages("ggpubr")
library(ggpubr)
ggscatter(data = retentiondata2, x = "OverageMinutes", y = "MonthlyRevenue",
          conf.int = TRUE, color="dark green", xlab="Overage Minutes used by customer", ylab="Monthly Revenue of the Telecom company", title="Scatter plot of Overage Minutes vs Monthly Revenue for retention customers")
```

The graph shows that even for customers who are still with the company, monthly revenue rises as Overage Minutes rise.
Also, we can observe that outliers are more for churned customers compared to non-churn customers


```{r, echo=T, results=T}
datacorr <- Telecom_Data[ , c("MonthlyRevenue","MonthlyMinutes", "TotalRecurringCharge","CustomerCareCalls","ThreewayCalls","ReceivedCalls","OutboundCalls","MonthsInService","HandsetPrice","CreditRating")]   
head(datacorr)
nrow(datacorr)
sum(is.na(datacorr))
```
There are 468 NA values in the subsetted dataset.

```{r, echo=T, results=T}
datacorr2 <- na.omit(datacorr)
nrow(datacorr2)
sum(is.na(datacorr2))
```

After removing the NA values, we are left out with 50891 rows.


Next, we have used few numerical factors, including months of service, outbound calls, received calls, three-way calls, customer care calls, total recurring calls, and monthly minutes, and we've conducted correlation statistical studies to look at how they relate to one another using correlation matrix. 
```{r, echo=T, results=T}
# load package
#install.packages("ggstatsplot")
#install.packages("ggcorrplot")

library(ggstatsplot)
library(ggcorrplot)
library(corrplot)

# correlogram
ggstatsplot::ggcorrmat(
  data = datacorr2,
  type = "nonparametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue"), 
  title = "Correlation matrix"
)

```

The above correlation graph leads us to the following conclusions:
  
  1. Monthly minutes consumed by the client and monthly revenue of the telecom operator are highly associated.
2. There is a significant probability that customers will receive calls from customer service.
3. The number of months a consumer stays with a service won't significantly alter its monthly revenue.
4. The customer service calls made by the telecom sector have no impact on the number of months the clients have left on their subscriptions.
