---
# This is the YAML header/metadata for the document
title: "Customer Churn Analysis"
author: "Pranav Chandaliya"

output:
  html_document:
    code_folding: hide
    number_sections: true
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r init, include=F}
# The package "ezids" (EZ Intro to Data Science) includes a lot of the helper functions we developed for the course. 
# Some of the frequently used functions are loadPkg(), xkabledply(), xkablesummary(), uzscale(), etc.
# Once installed, load the library.
library(ezids)
```


```{r setup, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# knitr::opts_chunk$set(include = F)
# knitr::opts_chunk$set(echo = TRUE)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```


Loading dataset 
```{r,results="show"}
telcm <- data.frame(read.csv("Telecom Data.csv"))
ncol(telcm)
nrow(telcm)
```
There are total 58 Columns and 51,047 Rows


Let's check for null values
```{r,results="show"}
library(dplyr)
library(tidyr)
## Checking the null values in the dataset
#summary(telcm)
#is.null(telcm)
null_values<-sapply(telcm, function(x) sum(is.na(x)))
null_values
```
Few columns have null values but the count is less,


Lets Create New Variables which will help in analysis 
```{r, results= "show"}
##Creation of new variables for our analysis
telcm$perc_recurrent_charge <- (telcm$TotalRecurringCharge /telcm$MonthlyRevenue) * 100

telcm$perc_overage_minute <- (telcm$OverageMinutes / telcm$MonthlyMinutes) * 100


str(telcm)





```


```{r,results="show"}
#install.packages("naniar")
#library(naniar)
#vis_miss(telcm,warn_large_data = FALSE)
#gg_miss_fct(x = riskfactors, fct = marital)

```

Lets calculate churn rate 
```{r,results="show"}
## Getting Churn counts 
churn_counts<- dplyr::count(telcm,Churn , sort = TRUE)
#pie(chrun_counts$n, labels = chrun_counts$Churn,explode = 0.1, main = "Pie Chart of Churn Rate ")
#pie(telcm$Churn)
```

Lets plot the churn rate using piechart

```{r,results="show"}
library("ggplot2")
ggplot(data = churn_counts, aes(x = "", y = n, fill = Churn)) + 
  geom_bar(stat = "identity") + 
  coord_polar("y")


```
Trying out plotly for pie chart for more interactive graphs 

```{r,results="show"}

library(plotly)
colors <- c('rgb(211,94,96)', 'rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(171,104,87)', 'rgb(114,147,203)')


fig <- plot_ly(type='pie', labels=churn_counts$Churn, values=churn_counts$n, 
               textinfo='label+percent',
               insidetextorientation='radial',marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))
fig


```

Subsetting data for in depth analysis on the basis of churn
and checking the summary of the divided data to analyze the trend
```{r,results="show"}
telcm$Churn <- factor(telcm$Churn)
library(dplyr)

telcm_yes = filter(telcm, Churn == "Yes")

telcm_no = filter(telcm, Churn == "No")

summary(telcm_yes)


summary(telcm_no)
``
`
```{r,results="show"}
summary(telcm_no)


```


```{r,results="show"}


```

```{r,results="show"}
feat_typ_counts <- data.frame(read.csv("Feat_type_counts.csv"))
#install.packages("plotrix")
library(plotrix)

library("ggplot2")
#pie(feat_typ_counts$Counts, feat_typ_counts$Variable.Type)

piepercent<- round(100 * feat_typ_counts$Counts / sum(feat_typ_counts$Counts), 1)


feat_typ_counts$fraction <- feat_typ_counts$Counts / sum(feat_typ_counts$Counts)

# Compute the cumulative percentages (top of each rectangle)
feat_typ_counts$ymax <- cumsum(feat_typ_counts$fraction)

# Compute the bottom of each rectangle
feat_typ_counts$ymin <- c(0, head(feat_typ_counts$ymax, n=-1))

# Compute label position
feat_typ_counts$labelPosition <- (feat_typ_counts$ymax + feat_typ_counts$ymin) / 2

# Compute a good label
feat_typ_counts$label <- paste0(feat_typ_counts$Variable.Type, "\n Count: ", feat_typ_counts$Counts)


ggplot(feat_typ_counts, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Variable.Type)) +
  geom_rect() +
  geom_label( x=3.5, aes(y=labelPosition, label=label), size=2) +
  scale_fill_brewer(palette=4) +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none")






```

```{r,results="show"}


xkablesummary(telcm)

```

```{r,results="show"}
boxplot(telcm$MonthlyMinutes,
main = "Monthly Minutes of Customers",
xlab = "Monthly Min",
ylab = "Frequency",
col = "orange",
border = "brown",
horizontal = TRUE,
notch = TRUE
)


```

##Current Headset use in days
```{r,results="show"}

plot_ly(telcm, y= telcm$CurrentEquipmentDays, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))

```
```{r,results="show"}
plot_ly(telcm, y= telcm$TotalRecurringCharge, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))


```
```{r,results="show"}
plot_ly(telcm, y= telcm$MonthsInService, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))


```
```{r,results="show"}
plot_ly(telcm, y= telcm$perc_recurrent_charge, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))


```

```{r,results="show"}
plot_ly(telcm, y= telcm$PercChangeMinutes, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))


```
```{r,results="show"}
plot_ly(telcm, y= telcm$PercChangeRevenues, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))


```
```{r,results="show"}
library(ggplot2)  
library(plotly)

set.seed(1)    

gg <- ggplot(telcm,aes(x = MonthlyRevenue, color = 'density')) +  
  geom_histogram(aes(y = ..density..), bins = 7,  fill = '#67B7D1', alpha = 0.5) +  
  geom_density(color = '#67B7D1') +  
  geom_rug(color = '#67B7D1') + 
  ylab("") + 
  xlab("")  + theme(legend.title=element_blank()) +
  scale_color_manual(values = c('density' = '#67B7D1'))


ggplotly(gg)%>% 
  layout(plot_bgcolor='#e5ecf6',   
             xaxis = list(   
               title='Time', 
               zerolinecolor = '#ffff',   
               zerolinewidth = 2,   
               gridcolor = 'ffff'),   
             yaxis = list(   
               title='Value A', 
               zerolinecolor = '#ffff',   
               zerolinewidth = 2,   
               gridcolor = 'ffff')) 

```

```{r,results="show"}
library(ggplot2)  
library(plotly)

set.seed(1)    

gg <- ggplot(telcm,aes(x = MonthlyMinutes, color = 'density')) +  
  geom_histogram(aes(y = ..density..), bins = 7,  fill = '#67B7D1', alpha = 0.5) +  
  geom_density(color = '#67B7D1') +  
  geom_rug(color = '#67B7D1') + 
  ylab("") + 
  xlab("")  + theme(legend.title=element_blank()) +
  scale_color_manual(values = c('density' = '#67B7D1'))


ggplotly(gg)%>% 
  layout(plot_bgcolor='#e5ecf6',   
             xaxis = list(   
               title='Monthly Minutes ', 
               zerolinecolor = '#ffff',   
               zerolinewidth = 2,   
               gridcolor = 'ffff'),   
             yaxis = list(   
               title='Frequency', 
               zerolinecolor = '#ffff',   
               zerolinewidth = 2,   
               gridcolor = 'ffff')) 




```


```{r,results="show"}
qqnorm(telcm$MonthlyMinutes)                        # QQplot 


qqline(telcm$MonthlyMinutes, col = "red") 
#install.packages("car")
#library("car")
#qqPlot(telcm$MonthlyMinutes)

```
```{r,results="show"}
library("plotly")
#plot_ly(telcm, y= telcm$AgeHH1, color = telcm$Churn, type = "box") 
         #layout(boxmode = "group", 
        # xaxis = list(title=''), 
        # yaxis = list(title='Frequency'))


```

```{r,results="show"}

## Anova Results 
one.way <- aov(MonthlyMinutes ~ Occupation, data = telcm)
#summary(one.way)
xkabledply(one.way, title = "ANOVA result summary")
```
```{r,results="show"}
plot_ly(telcm, y= telcm$perc_recurrent_charge, color = telcm$Churn, type = "box") %>% 
         layout(boxmode = "group", 
         xaxis = list(title=''), 
         yaxis = list(title='Frequency'))

